---
title: "Vivekn Sentiment Analysis"
output: html_notebook
---

This notebook is adapted from John Snow Labs workshop Jupyter/Python tutorial "ViveknNarayanSentimentApproach.ipynb"
(https://github.com/JohnSnowLabs/spark-nlp-workshop/blob/master/jupyter/training/english/vivekn-sentiment/VivekNarayanSentimentApproach.ipynb)

In the following example, we walk-through Sentiment Analysis training and prediction using Spark NLP Annotators.

The ViveknSentimentApproach annotator will compute Vivek Narayanan algorithm with either a column in training dataset 
with rows labelled 'positive' or 'negative' or a folder full of positive text and a folder with negative text. Using 
n-grams and negation of sequences, this statistical model can achieve high accuracy if trained properly.

Spark can be leveraged in training by utilizing ReadAs.Dataset setting. Spark will be used during prediction by default.

We also include in this pipeline a spell checker which shall correct our sentences for better Sentiment Analysis accuracy.

### 1. Call necessary imports and set the resource path to read local data files¶
```{r}
library(sparklyr)
library(sparknlp)
library(dplyr)
```

### 2. Load SparkSession if not already there
```{r}
version <- Sys.getenv("SPARK_VERSION", unset = "2.4.0")

config <- sparklyr::spark_config()
config$`sparklyr.shell.driver-memory` <- "8g"

options(sparklyr.sanitize.column.names.verbose = TRUE)
options(sparklyr.verbose = TRUE)
options(sparklyr.na.omit.verbose = TRUE)
options(sparklyr.na.action.verbose = TRUE)
sc <- sparklyr::spark_connect(master = "local[*]", version = version, config = config)
```

```{r}
temp_dir <- tempdir()

download.file("https://s3.amazonaws.com/auxdata.johnsnowlabs.com/public/resources/en/spell/words.txt", destfile = paste0(temp_dir, "/words.txt"))
download.file("https://s3.amazonaws.com/auxdata.johnsnowlabs.com/public/resources/en/sentiment.parquet.zip", destfile = paste0(temp_dir, "/sentiment_parquet.zip"))
unzip(paste0(temp_dir, "/sentiment_parquet.zip"), exdir = temp_dir)
```

### 3. Load a spark dataset and put it in memory
```{r}
data <- spark_read_parquet(sc, paste0(temp_dir, "/sentiment.parquet")) %>%
  mutate(sentiment_label = if_else(sentiment == 0, "negative", "positive")) %>%
  head(1000) %>%
  sdf_register(name = "data")

tbl_cache(sc, "data")

head(data)
```
### 4. Create the document assembler, which will put target text column into Annotation form
```{r}
document_assembler <- nlp_document_assembler(sc, input_col = "text", output_col = "document")
assembled = ml_transform(document_assembler, data)
head(assembled, n = 5)
```
### 5. Create Sentence detector to parse sub sentences in every document
```{r}
sentence_detector <- nlp_sentence_detector(sc, input_cols = c("document"), output_col = "sentence")
sentence_data <- ml_transform(sentence_detector, assembled)
head(sentence_data, n = 5)
```
### 6. The tokenizer will match standard tokens
```{r}
tokenizer <- nlp_tokenizer(sc, input_cols = c("sentence"), output_col = "token")
tokenized <- ml_fit_and_transform(tokenizer, sentence_data)
head(tokenized, n = 5)
```
### 7. Normalizer will clean out the tokens
```{r}
normalizer <- nlp_normalizer(sc, input_cols = c("token"), output_col = "normal")
```
### 8. The spell checker will correct normalized tokens, this trains with a dictionary of english words
```{r}
spell_checker <- nlp_norvig_spell_checker(sc, input_cols = c("normal"), output_col = "spell", dictionary_path = paste0(temp_dir, "/words.txt"))
```
### 9. Create the ViveknSentimentApproach and set resources to train it
```{r}
sentiment_detector <- nlp_vivekn_sentiment_detector(sc, input_cols = c("spell", "sentence"), output_col = "sentiment", 
                                           sentiment_col = "sentiment_label", prune_corpus = 0)
```
### 10. The finisher will utilize sentiment analysis output
```{r}
finisher = nlp_finisher(sc, input_cols = c("sentiment"), include_metadata = FALSE)
```
### 11. Fit and predict over data
```{r}
pipeline <- ml_pipeline(
  document_assembler,
  sentence_detector,
  tokenizer,
  normalizer,
  spell_checker,
  sentiment_detector,
  finisher
)

start <- Sys.time()
sentiment_data <- ml_fit_and_transform(pipeline, data)
end <- Sys.time()
print(paste0("Time elapsed pipeline process:", end - start))
```
### 13. Check the result
```{r}
head(sentiment_data, n = 5)
```
```{r}
class(sentiment_data)
```
```{r}
# Negative sentiments
negatives <- sentiment_data %>%
  filter(array_contains(finished_sentiment, "negative")) %>%
  head(n = 5) %>%
  collect()

negatives %>%
  mutate(finished_sentiment = purrr::map_chr(finished_sentiment, function(s) paste(s, collapse = ", "))) %>%
  select(text, finished_sentiment)
```
```{r}
# Positive sentiments
positives <- sentiment_data %>%
  filter(array_contains(finished_sentiment, "positive")) %>%
  head(n = 5) %>%
  collect()

positives %>%
  mutate(finished_sentiment = purrr::map_chr(finished_sentiment, function(s) paste(s, collapse = ", "))) %>%
  select(text, finished_sentiment)
```