---
title: "Spark NLP Quick Start"
output: html_notebook
---


This notebook is adapted from John Snow Labs Jupyter/Python getting started notebook. See https://github.com/JohnSnowLabs/spark-nlp-workshop/blob/master/jupyter/quick_start.ipynb for that version.

# Spark NLP Quick Start
## How to use Spark NLP pretrained pipelines
Make sure you have already installed sparklyr and sparklnlp

```{r}
library(dplyr)
library(sparklyr)
library(sparknlp)
```

### Let's create a Spark Session for our app
```{r}
version <- Sys.getenv("SPARK_VERSION", unset = "2.4.0")

config <- sparklyr::spark_config()
    
options(sparklyr.sanitize.column.names.verbose = TRUE)
options(sparklyr.verbose = TRUE)
options(sparklyr.na.omit.verbose = TRUE)
options(sparklyr.na.action.verbose = TRUE)
sc <- sparklyr::spark_connect(master = "local", version = version, config = config)
```

Let's use Spark NLP pre-trained pipeline for named entity recognition
```{r}
pipeline <- nlp_pretrained_pipeline(sc, "recognize_entities_dl", lang = "en")
```

```{r}
result <- nlp_annotate(pipeline, "Google has announced the release of a beta version of the popular TensorFlow machine learning library.")
```

```{r}
ner_list <- result %>% pull(ner)
unlist(purrr::map(ner_list, function(l1) purrr::map(l1, function(l) l[[4]])))
```
```{r}
entities_list <- result %>% pull(entities)
unlist(purrr::map(entities_list, function(l1) purrr::map(l1, function(l) l[[4]])))
```

Let's use Spark NLP pre-trained pipeline for sentiment analysis
```{r}
pipeline <- nlp_pretrained_pipeline(sc, "analyze_sentiment", "en")
```

```{r}
result <- nlp_annotate(pipeline, "This is a very boring movie. I recommend others to awoid this movie is not good..")
```

```{r}
sent_list <- result %>% pull(sentiment)
unlist(purrr::map(sent_list, function(l1) purrr::map(l1, function(l) l[[4]])))
```

```{r}
checked_list <- result %>% pull(checked)
unlist(purrr::map(checked_list, function(l1) purrr::map(l1, function(l) l[[4]])))
```

The word awoid has been corrected to avoid by spell checker inside this pipeline
